Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-15 report/report.tex
Add definiton of roads and footpaths

@@

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM building dataset and the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for an implementation overview, 3.2 for a walkthrough of the program implementation, and 4.1.2 for the results.

@@

% NOW-NOW:
% TODO: Make clear that a footpath is a type of road. Even sidewalks that run along main roads are classified as roads in OSM.
% TODO: Use overlap instead of collision outside of technical contexts

% NOW:
% TODO: Introduce concepts: Collision, overlap, error
% TODO: Come up with a sentence that explains why errors could cause overlap. Repeat it in Introduction, research question and the abstract
% TODO: The word footpath does not appear anywhere in the TOC

>>>>

This project will strive to determine the feasibility of procuderally reconstructing a city road network from OSM data by using such models as have been mentioned in this section, focusing on pedestrian footpaths.
\textbf{Footpaths} include any form of path that is designated for pedestrians, including sidewalks, walkways and trails.
OSM commonly divides city road networks into any of the following 4 categories: arterial (primary) roads, secondary roads, residential roads and footpaths.
For the purpose of this report, a \textbf{road} will be any road whose primary use is human travel, either via a vehicle or by foot.
Note that by this definition even sidewalks are classifed as roads, even though they commonly run in connection to larger roads (which are usually reserved for motor vehicles), and thus may not always be thought of as roads in plain language.

@@

For the secondary research question: the geodata precision study, the positional accuracy will be estimated by comparing feature points between the OSM building dataset and the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy. See section 3.4.2 for an overview of the SLU dataset and how it is obtained.
The positional accuracy will be needed to assess where road collisions occur and whether they can easily be corrected.
For the positional accuracy study, see sections 3.1.1 for an implementation overview, 3.2 for a walkthrough of the program implementation, and 4.1.2 for the results.

@@

% NOW:
% TODO: Use overlap instead of collision outside of technical contexts
% TODO: Introduce concepts: Collision, overlap, error
% TODO: Come up with a sentence that explains why errors could cause overlap. Repeat it in Introduction, research question and the abstract
% TODO: The word footpath does not appear anywhere in the TOC
